---
title: "R for repruducible science"
author: "EvB"
date: "4/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(123)   # Makes it reproduceable even if random number generators are used

```

## Background

```{r setup}
#load packages & data
library(rethinking)
library(rstan)
library(tidyverse)
library(brms)
source("src/functions.r")
```

<br>
<br>
## 1. Data processing

#### 1. 1 Remove extra participants
First, because of an error when sending the study out, a whole bunch of participants did the experiment twice. The following section makes frequent use of the recode() command. The datafile contains numerical data coded as strings. While I was at it, I also calculated 

```{r recoding, echo=FALSE}
d <- d <- read.csv("https://raw.githubusercontent.com/vanbrrlekom/Categorization/main/data/categorization1_data.csv", na.strings = "")%>% 
  mutate(dupe = duplicated(IPAddress)) %>% #Checks if IP adress has occurred previously
  filter(dupe == FALSE) %>%  # removes duplicated IP adresses
  mutate( across(starts_with("ess"),  # changes responses to numerical
                  ~recode(.,"Stämmer inte alls\n1" ="1",
                          "Stämmer helt\n7" = "7") %>% as.integer()),
          across(starts_with("hen_attitudes"),
                 ~recode(.,"Mycket bra\n7" ="1",
                          "Mycket dåligt\n1" = "7") %>% as.integer()),
          across(starts_with("GIS"),  # changes responses to numerical
                  ~recode(.,"Stämmer inte alls\n1" ="1",
                          "Stämmer helt\n7" = "7") %>% as.integer()), id = row_number(),
          hen_use = 
           recode(hen_use,
                  "Aldrig" = 1,
                  "Någon gång om året" = 2,
                  "Någon gång i månaden" = 3,
                  "Någon gång per vecka" = 4,
                  "Dagligen" = 5) %>% as.integer(),
         hen_hear = 
           recode(hen_hear,
                  "Aldrig" = 1,
                  "Någon gång om året" = 2,
                  "Någon gång i månaden" = 3,
                  "Någon gång per vecka" = 4,
                  "Dagligen" = 5) %>%  as.integer()) %>% 
  rename(id_feminist = essentialism_7 ,id_lgbtq = essentialism_8)
  
```

#### 1.2 Check to make sure all participants completed the experiment

The aim of the experiment was to investigate the effect of pronoun use on gender categorization of faces. First, then, participants completed a task where they used a pronoun three times. The following code checks whether participants used the correct pronoun three times. If they didn't they are assigned a NA value

```{r}
d <- manipulation_check(d)
```


#### 1.3 Clean up variables

We also collected survey data on some personal attitudes. Gender essentialism (essentialism), Gender identity strength and attitudes to the word hen. These were multi-item questionnaires. The following chunk calculates the mean scores for each scale and standardizes them

```{r essentialism & other variables}
# takes a variable & standardized is

d <- d %>% 
  mutate(essentialism_s = rowMeans(select(d, starts_with("essentialism"))) %>% standardize(),
         GIS_s= rowMeans(select(d, starts_with("GIS"))) %>% standardize(),
         hen_attitudes_s= rowMeans(select(d, starts_with("hen_attitudes"))) %>% standardize())
         
```


#### 1.4 reshaping

The following chunk selects the relevant columns, the standardized scores, and the responses and melts it all into a long-format data-frame.

```{r}
#Select only the relevant columns
d <- d %>% 
  select(essentialism_s, GIS_s, hen_attitudes_s, hen_use, hen_hear, id_feminist, id_lgbtq,
         starts_with("X"), id, condition) %>% 
  pivot_longer(cols = contains("X"), names_to = "face", values_to = "categorization")%>% 
  mutate(resp = recode(categorization, 
                       "Icke-binär" = "NB",
                       "Man" = "B", 
                       "Kvinna" = "B",
                       "Vet ej" = "NB"))
```

## 2 Analysis
Model specification. 
```{r}

prior1 <- c(
  prior(normal(0, 1.5), class = Intercept),
  prior(normal(0, 0.5), class = b), 
  prior(cauchy(0, 3), class = sd)
)

cat_multilevel_m1 <- brm(
  resp ~ essentialism_s * condition + (1|id) + (1|face), 
  family = bernoulli("logit"),
  prior = prior1,
  data = d, 
  warmup = 2000, iter = 5000, file = "models/cat_multilevel_m1"
)
```

